---
title: "MANOVA-equalcovars"
output:
  word_document: default
  html_document: default
date: "2022-08-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
FROM ANN:

For MANOVA (= formal analysis), may want to think about how to use “other” or “no answer” categories.
Also consider whether you want to include all interactions.
If you do, consider the combination of the two issues above.   
 
When retaining “other” and “no answer” categories, there are a total of
3 genders (including 14 Other)
5 races (including 29 Other)
3 age groups
This yields a total of 3*5*3 = 45 possible combinations, but only observe 35 total combinations.  Some of those combinations include only 1-2 people.


ADDITIVE MODEL WAS SUGGESTED BY ANN 

 
Use summary() to get tests corresponding to predictors.
For MANOVA there are several possible methods for testing.   
 
Personally, I would not worry about doing Box’s test.  You might mention the corresponding assumption, but I am not inclined to do a formal test.   Or if you really do want to run it, perhaps do it separately by each factor (gender, race, age_group).  



MY NOTES:

To check normality:
QQ plot (A Q-Q plot or Quantile-Quantile plot is a common graphical way to check data for non-normality. Quantile is another term for percentile. A Q-Q plot is a plot of the quantiles of a data set versus the quantiles of a reference theoretical distribution. This plot is used to assess normality of residuals. Curvature and outliers indicate problems. Note: The QQ plot is not useful until variance is
approximately equal.)

shapiro.test with p value greater than 0.05 (Histograms and QQ plots are usually more informative than the tests, because small sample sizes generally “pass” the test (high p-value, no evidence against normality), and large sample sizes generally “fail” (small p-value, evidence against normality).)


To check homogeneity of covariances/equal variance:

Box's test (homegeneity of variance-covariance matrices)

Levene’s test of equality of variances (homogeneity of variances)

Plot of residuals vs fitted values (equal scatter; This is the primary diagnostic plot for assessing linearity and constant
variance. Curvature, unequal variance (megaphone) or outliers indicate problems.)



To check linear response:

Plot of resids vs fitted values (should not show a trend)

Look to pages 20-end 512 MultReg1



For y variables: You should have an adequate sample size. Although the larger your sample size, the better, at a bare minimum, there needs to be as many cases (e.g., particpants) in each cell of the design as there are number of dependent variables. 12 dependent variables


For MANOVA, the dependent variables should be somewhat correlated. 



STEPS: 
Power analysis to find sample size - 278
NAs shouldn't be over 20% 
Find outliers & remove (see removing stat outliers or MANOVA imputing)
Double check correlations
check assumptions 
run manova
run anovas



```{r packages}
library(tidyverse)
library(readxl)
library(flextable)
library(extrafont)
library(writexl)
library(corrr)
library(corrplot)
library(heplots) #boxM function
library(DFA.CANCOR)
```





```{r}
#times new roman tables
my_ft_theme <- function(ft, ...) {
  # Remove vertical cell padding
  ft <- padding(ft, padding.top = 0, padding.bottom = 0, part = "all")
  
  # Change font to TNR 11
  ft <- font(ft, fontname = "Times New Roman", part = "all")
  ft <- fontsize(ft, part = "all", size = 12)
  ft
}
```



```{r}
SA3_noout <- read_excel("C:\\Users\\kayna\\Documents\\headscan_dissertation\\chosen_nona1.xlsx")
```


```{r}
str(SA3_noout)
SA3_num <- select_if(SA3_noout, is.numeric)
```


```{r}
correl <- correlate(SA3_num)
correl
```


```{r, fig.height=6, fig.width=8}
correl2 <- cor(SA3_num)
symnum(correl2)
corrplot(correl2, method = 'number')
```












Checking assumptions on actual MANOVA model: setup

```{r}
variables <- cbind(SA3_noout$AA_C, SA3_noout$BiW_C, SA3_noout$BiW_L, 
                   SA3_noout$GoSub_C, SA3_noout$NRB_L, SA3_noout$ProS_L,
                   SA3_noout$SelP_L, SA3_noout$SelM_L, SA3_noout$SnasM_C,
                   SA3_noout$TrSman_C, SA3_noout$TrTr_C, SA3_noout$TrTr_L)


#part of Dr. Erin Buchanan's lecture, but Manova code returns error: Error in Anova.mlm(mod, ...) : model is singular
#lm_notransf <- lm(variables ~ gender+race_eth+age_group, data=SA3_noout,
                  #contrasts = list(gender=contr.sum, 
                                   #race_eth=contr.sum,
                                   #age_group=contr.sum))

#manova_notransf <- Manova(lm_notransf, type = "III")

```



Checking assumptions on actual MANOVA model: no transformation

```{r}



manova_out_nt <- manova(variables ~ gender+race_eth+age_group, data=SA3_noout)
fitted1 <- manova_out_nt$fitted.values
resid1 <- rstandard(manova_out_nt)

#homogeneity (unscaled)
plot(fitted1, resid1)
abline(0,0)
abline(v = 0)

#linearity
qqnorm(resid1)
abline(0,1, lty=2)

#normality
hist(resid1)
```


```{r}
#creating dataframe for ggplot
fitted1.1 <- as.data.frame(fitted1)
resid1.1 <-as.data.frame(resid1)

fitted1.1 <- rownames_to_column(fitted1.1, "scan_num")

fitted1.1 <- pivot_longer(fitted1.1, V1:V12, names_to = "variable", values_to = "fitted_vals")


resid1.1 <- rownames_to_column(resid1.1, "scan_num")

resid1.1 <- pivot_longer(resid1.1, V1:V12, names_to = "variable", values_to = "resid_vals")



temp5 <- full_join(fitted1.1, resid1.1, by=c('scan_num', 'variable'))
str(temp5)
```

THIS is the model for reporting, and for use in MANOVA. 

```{r}
ggplot(data=temp5, aes(x=fitted_vals, y=resid_vals))+
  geom_point(shape=1)+
  geom_hline(yintercept=0)+  
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="Residuals vs. Fitted Values of Manova Model",
       y= "Standardized Residuals",
       x= "Fitted Values")

ggplot(data=temp5, aes(sample=resid_vals))+
  stat_qq()+
  stat_qq_line()+
  scale_x_continuous(n.breaks = 7)+
  #xlim(-3.5,3.5)+
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="QQPlot of Manova Model",
       y= "Sample Quantiles",
       x= "Theoretical Quantities")

ggplot(data=temp5, aes(x=resid_vals))+
  geom_bar(stat="bin", bins=20, color= "black", fill = "white")+
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="Normality of Manova Model",
       y= "Count",
       x= "Standardized Residuals")
```
```{r}
boxM( cbind(AA_C, BiW_C, BiW_L, GoSub_C, NRB_L, ProS_L,
           SelP_L, SelM_L, SnasM_C,  
           TrSman_C, TrTr_C, TrTr_L) ~ race_eth, data=SA3_noout)

boxM( cbind(AA_C, BiW_C, BiW_L, GoSub_C, NRB_L, ProS_L,
           SelP_L, SelM_L, SnasM_C,
           TrSman_C, TrTr_C, TrTr_L) ~ gender, data=SA3_noout)

boxM( cbind(AA_C, BiW_C, BiW_L, GoSub_C, NRB_L, ProS_L,
           SelP_L, SelM_L, SnasM_C,
           TrSman_C, TrTr_C, TrTr_L) ~ age_group, data=SA3_noout)

SA3_noout$gender <- as.factor(SA3_noout$gender)
SA3_noout$race_eth <- as.factor(SA3_noout$race_eth)
SA3_noout$age_group <- as.factor(SA3_noout$age_group)

summary(SA3_noout)

boxtest_data <- SA3_noout

boxtest_data$gender <-
  recode_factor(boxtest_data$gender, 'Female'= "Female/Other",
                'Other' = "Female/Other")

boxM( cbind(AA_C, BiW_C, BiW_L, GoSub_C, NRB_L, ProS_L,
           SelP_L, SelM_L, SnasM_C,
           TrSman_C, TrTr_C, TrTr_L) ~ gender, data=boxtest_data)
```


Box’s M test the assumption of equality of covariance matrices. However, Box's M is sensitive to large data files; therefore, it can detect even small departures from homogeneity. Moreover, it can be sensitive to departures from the assumption of normality.

Box's M:  If group sizes are over 30, then the MANOVA is robust against violations of homogeneity of variance-covariance matrices assumption.
Levene's Test:     if homogeneity of variance can't be assumed for one (or more) dependent variables, then use an alpha level stricter than .05 (ie: use .001) when you evaluate the univariate ANOVAs.
[From "SPSS for the Health and Behavioural Sciences" (Allen & Bennett, 2008)]


Huberty, C. J, & Morris, J. D. (1989). Multivariate analysis versus multiple univariate analyses. Psychological Bulletin, 105, 302-308.

https://www.researchgate.net/post/What-if-the-Boxs-Test-in-two-way-MANOVA-is-significant




#don't really see the point of doing transformations, they didn't affect too much for visual assumptions or Levene's test












```{r}
HOMOGENEITY(data=SA3_noout, groups='race_eth', variables=c('AA_C', 'BiW_C', 
                                                           'BiW_L', 'GoSub_C',
                                                           'NRB_L', 'ProS_L',
                                                           'SelP_L', 'SelM_L', 
                                                           'SnasM_C','TrSman_C', 
                                                           'TrTr_C', 'TrTr_L'))
```
```{r}
HOMOGENEITY(data=SA3_noout, groups='gender', variables=c('AA_C', 'BiW_C', 
                                                           'BiW_L', 'GoSub_C',
                                                           'NRB_L', 'ProS_L',
                                                           'SelP_L', 'SelM_L', 
                                                           'SnasM_C', 'TrSman_C', 
                                                         'TrTr_C', 'TrTr_L'))
```
```{r}
HOMOGENEITY(data=SA3_noout, groups='age_group', variables=c('AA_C', 'BiW_C', 
                                                           'BiW_L', 'GoSub_C',
                                                           'NRB_L', 'ProS_L',
                                                           'SelP_L', 'SelM_L', 
                                                           'SnasM_C', 'TrSman_C', 
                                                           'TrTr_C', 'TrTr_L'))
```




```{r}
boxtest_data <- column_to_rownames(SA3_noout, "ID")

boxtest_data$race_eth <-
  recode_factor(boxtest_data$race_eth, 'LatinX'= "Other",
                'Asian' = "Other")

boxtest_data$gender <-
  recode_factor(boxtest_data$gender, 'Female'= "Female or Other",
                'Other' = "Female or Other")

boxtest_data <- boxtest_data %>% drop_na()

boxtest_data$age_group <- as.factor(boxtest_data$age_group)

summary(boxtest_data)

boxM( cbind(AA_C, BiW_C, BiW_L, GoSub_C, NRB_L, ProS_L,
           SelP_L, SelM_L, SnasM_C, 
           TrSman_C, TrTr_C, TrTr_L) ~ race_eth, data=boxtest_data)

boxM( cbind(AA_C, BiW_C, BiW_L, GoSub_C, NRB_L, ProS_L,
           SelP_L, SelM_L, SnasM_C, 
           TrSman_C, TrTr_C, TrTr_L) ~ gender, data=boxtest_data)

boxM( cbind(AA_C, BiW_C, BiW_L, GoSub_C, NRB_L, ProS_L,
           SelP_L, SelM_L, SnasM_C,
           TrSman_C, TrTr_C, TrTr_L) ~ age_group, data=boxtest_data)


```
```{r}
HOMOGENEITY(data=boxtest_data, groups='race_eth', variables=c('AA_C', 'BiW_C', 
                                                           'BiW_L', 'GoSub_C',
                                                           'NRB_L', 'ProS_L',
                                                           'SelP_L', 'SelM_L', 
                                                           'SnasM_C', 'TrSman_C', 
                                                           'TrTr_C', 'TrTr_L'))
#```

#```{r}
HOMOGENEITY(data=boxtest_data, groups='gender', variables=c('AA_C', 'BiW_C', 
                                                           'BiW_L', 'GoSub_C',
                                                           'NRB_L', 'ProS_L',
                                                           'SelP_L', 'SelM_L', 
                                                           'SnasM_C', 'TrSman_C', 
                                                           'TrTr_C', 'TrTr_L'))
```

```{r}
HOMOGENEITY(data=boxtest_data, groups='age_group', variables=c('AA_C', 'BiW_C', 
                                                           'BiW_L', 'GoSub_C',
                                                           'NRB_L', 'ProS_L',
                                                           'SelP_L', 'SelM_L', 
                                                           'SnasM_C', 'TrSman_C', 
                                                           'TrTr_C', 'TrTr_L'))
```


Box’s M test the assumption of equality of covariance matrices. However, Box's M is sensitive to large data files; therefore, it can detect even small departures from homogeneity. Moreover, it can be sensitive to departures from the assumption of normality.

Box's M:  If group sizes are over 30, then the MANOVA is robust against violations of homogeneity of variance-covariance matrices assumption.
Levene's Test:     if homogeneity of variance can't be assumed for one (or more) dependent variables, then use an alpha level stricter than .05 (ie: use .001) when you evaluate the univariate ANOVAs.
[From "SPSS for the Health and Behavioural Sciences" (Allen & Bennett, 2008)]


Huberty, C. J, & Morris, J. D. (1989). Multivariate analysis versus multiple univariate analyses. Psychological Bulletin, 105, 302-308.
