---
title: "MANOVA assumptions"
output: html_document
date: "2022-08-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse)
library(readxl)
library(flextable)
library(extrafont)
library(corrr) #correlate function
library(corrplot) #corrplot
```





```{r}
#times new roman tables
my_ft_theme <- function(ft, ...) {
  # Remove vertical cell padding
  ft <- padding(ft, padding.top = 0, padding.bottom = 0, part = "all")
  
  # Change font to TNR 11
  ft <- font(ft, fontname = "Times New Roman", part = "all")
  ft <- fontsize(ft, part = "all", size = 12)
  ft
}
```



```{r}
SA3_noout <- read_excel("C:\\Users\\kayna\\Documents\\headscan_dissertation\\chosen_nona1.xlsx")
```


```{r}
str(SA3_noout)
SA3_num <- select_if(SA3_noout, is.numeric)
```


```{r}
correl <- correlate(SA3_num)
correl
```


```{r, fig.height=6, fig.width=8}
correl2 <- cor(SA3_num)
symnum(correl2)
corrplot(correl2, method = 'number')
```












Checking assumptions on actual MANOVA model: setup

```{r}
variables <- cbind(SA3_noout$AA_C, SA3_noout$BiW_C, SA3_noout$BiW_L, 
                   SA3_noout$GoSub_C, SA3_noout$NRB_L, SA3_noout$ProS_L,
                   SA3_noout$SelP_L, SA3_noout$SelM_L, SA3_noout$SnasM_C,
                   SA3_noout$TrSman_C, SA3_noout$TrTr_C, SA3_noout$TrTr_L)


#part of Dr. Erin Buchanan's lecture, but Manova code returns error: Error in Anova.mlm(mod, ...) : model is singular
#lm_notransf <- lm(variables ~ gender+race_eth+age_group, data=SA3_noout,
                  #contrasts = list(gender=contr.sum, 
                                   #race_eth=contr.sum,
                                   #age_group=contr.sum))

#manova_notransf <- Manova(lm_notransf, type = "III")

```



Checking assumptions on actual MANOVA model: no transformation

```{r}



manova_out_nt <- manova(variables ~ gender+race_eth+age_group, data=SA3_noout)
fitted1 <- manova_out_nt$fitted.values
resid1 <- rstandard(manova_out_nt)

#homogeneity (unscaled)
#plot(fitted1, resid1)
#abline(0,0)
#abline(v = 0)

#linearity
#qqnorm(resid1)
#abline(0,1, lty=2)

#normality
#hist(resid1)
```


```{r}
#creating dataframe for ggplot
fitted1.1 <- as.data.frame(fitted1)
resid1.1 <-as.data.frame(resid1)

fitted1.1 <- rownames_to_column(fitted1.1, "scan_num")

fitted1.1 <- pivot_longer(fitted1.1, V1:V12, names_to = "variable", values_to = "fitted_vals")


resid1.1 <- rownames_to_column(resid1.1, "scan_num")

resid1.1 <- pivot_longer(resid1.1, V1:V12, names_to = "variable", values_to = "resid_vals")



temp5 <- full_join(fitted1.1, resid1.1, by=c('scan_num', 'variable'))
str(temp5)
```

THIS is the model for reporting, and for use in MANOVA. 

```{r}
ggplot(data=temp5, aes(x=fitted_vals, y=resid_vals))+
  geom_point(shape=1)+
  geom_hline(yintercept=0)+  
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="Residuals vs. Fitted Values of Manova Model",
       subtitle = "No Transformation",
       y= "Standardized Residuals",
       x= "Fitted Values")

ggplot(data=temp5, aes(sample=resid_vals))+
  stat_qq()+
  stat_qq_line()+
  scale_x_continuous(n.breaks = 7)+
  #xlim(-3.5,3.5)+
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="QQPlot of Manova Model",
       subtitle = "No Transformation",
       y= "Sample Quantiles",
       x= "Theoretical Quantities")

ggplot(data=temp5, aes(x=resid_vals))+
  geom_bar(stat="bin", bins=20, color= "black", fill = "white")+
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="Normality of Manova Model",
       subtitle = "No Transformation",
       y= "Count",
       x= "Standardized Residuals")
```








Checking assumptions on actual MANOVA model: log base 10 transformation

```{r}

manova_out_log10 <- manova(log(variables, base=10) ~ gender+race_eth+age_group, data=SA3_noout)


fitted1_log10 <- manova_out_log10$fitted.values

resid1_log10 <- rstandard(manova_out_log10)


#homogeneity 
#plot(fitted1_log10, resid1_log10)
#abline(0,0)
#abline(v = 0)

#linearity
#qqnorm(resid1_log10)
#abline(0,1, lty=2)

#normality
#hist(resid1_log10)
```

```{r}
#creating dataframe for ggplot
fitted2.1 <- as.data.frame(fitted1_log10)
resid2.1 <-as.data.frame(resid1_log10)

fitted2.1 <- rownames_to_column(fitted2.1, "scan_num")

fitted2.1 <- pivot_longer(fitted2.1, V1:V12, names_to = "variable", values_to = "fitted_vals")


resid2.1 <- rownames_to_column(resid2.1, "scan_num")

resid2.1 <- pivot_longer(resid2.1, V1:V12, names_to = "variable", values_to = "resid_vals")



temp6 <- full_join(fitted2.1, resid2.1, by=c('scan_num', 'variable'))
str(temp6)
```

```{r}
ggplot(data=temp6, aes(x=fitted_vals, y=resid_vals))+
  geom_point(shape=1)+
  geom_hline(yintercept=0)+  
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="Residuals vs. Fitted Values of Manova Model",
       subtitle = "Log Base 10 Transformation",
       y= "Standardized Residuals",
       x= "Fitted Values")

ggplot(data=temp6, aes(sample=resid_vals))+
  stat_qq()+
  stat_qq_line()+
  scale_x_continuous(n.breaks = 7)+
  #xlim(-3.5,3.5)+
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="QQPlot of Manova Model",
       subtitle = "Log Base 10 Transformation",
       y= "Sample Quantiles",
       x= "Theoretical Quantities")

ggplot(data=temp5, aes(x=resid_vals))+
  geom_bar(stat="bin", bins=20, color= "black", fill = "white")+
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="Normality of Manova Model",
       subtitle = "Log Base 10 Transformation",
       y= "Count",
       x= "Standardized Residuals")
```




Checking assumptions on actual MANOVA model: log transformation

```{r}

manova_out_log <- manova(log(variables) ~ gender+race_eth+age_group, data=SA3_noout)


fitted1_log <- manova_out_log$fitted.values

resid1_log <- rstandard(manova_out_log)


#homogeneity
plot(fitted1_log, resid1_log)
abline(0,0)
abline(v = 0)

#linearity
qqnorm(resid1_log)
abline(0,1, lty=2)

#normality
hist(resid1_log)
```

```{r}
#creating dataframe for ggplot
fitted3.1 <- as.data.frame(fitted1_log)
resid3.1 <-as.data.frame(resid1_log)

fitted3.1 <- rownames_to_column(fitted3.1, "scan_num")

fitted3.1 <- pivot_longer(fitted3.1, V1:V12, names_to = "variable", values_to = "fitted_vals")


resid3.1 <- rownames_to_column(resid3.1, "scan_num")

resid3.1 <- pivot_longer(resid3.1, V1:V12, names_to = "variable", values_to = "resid_vals")



temp7 <- full_join(fitted3.1, resid3.1, by=c('scan_num', 'variable'))
str(temp7)
```

```{r}
ggplot(data=temp7, aes(x=fitted_vals, y=resid_vals))+
  geom_point(shape=1)+
  geom_hline(yintercept=0)+  
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="Residuals vs. Fitted Values of Manova Model",
       subtitle = "Log e Transformation",
       y= "Standardized Residuals",
       x= "Fitted Values")

ggplot(data=temp7, aes(sample=resid_vals))+
  stat_qq()+
  stat_qq_line()+
  scale_x_continuous(n.breaks = 7)+
  #xlim(-3.5,3.5)+
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="QQPlot of Manova Model",
       subtitle = "Log e Transformation",
       y= "Sample Quantiles",
       x= "Theoretical Quantities")

ggplot(data=temp7, aes(x=resid_vals))+
  geom_bar(stat="bin", bins=20, color= "black", fill = "white")+
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="Normality of Manova Model",
       subtitle = "Log e Transformation",
       y= "Count",
       x= "Standardized Residuals")
```




Checking assumptions on actual MANOVA model: sqrt transformation

```{r}

manova_out_sqrt <- manova(sqrt(variables) ~ gender+race_eth+age_group, data=SA3_noout)

fitted1_sqrt <- manova_out_sqrt$fitted.values

resid1_sqrt <- rstandard(manova_out_sqrt)

#homogeneity 
plot(fitted1_sqrt, resid1_sqrt)
abline(0,0)
abline(v = 0)

#linearity
qqnorm(resid1_sqrt)
abline(0,1, lty=2)

#normality
hist(resid1_sqrt)
```

```{r}
#creating dataframe for ggplot
fitted4.1 <- as.data.frame(fitted1_sqrt)
resid4.1 <-as.data.frame(resid1_sqrt)

fitted4.1 <- rownames_to_column(fitted4.1, "scan_num")

fitted4.1 <- pivot_longer(fitted4.1, V1:V12, names_to = "variable", values_to = "fitted_vals")


resid4.1 <- rownames_to_column(resid4.1, "scan_num")

resid4.1 <- pivot_longer(resid4.1, V1:V12, names_to = "variable", values_to = "resid_vals")



temp8 <- full_join(fitted4.1, resid4.1, by=c('scan_num', 'variable'))
str(temp8)
```

```{r}
ggplot(data=temp8, aes(x=fitted_vals, y=resid_vals))+
  geom_point(shape=1)+
  geom_hline(yintercept=0)+  
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="Residuals vs. Fitted Values of Manova Model",
       subtitle = "Square Root Transformation",
       y= "Standardized Residuals",
       x= "Fitted Values")

ggplot(data=temp8, aes(sample=resid_vals))+
  stat_qq()+
  stat_qq_line()+
  scale_x_continuous(n.breaks = 7)+
  #xlim(-3.5,3.5)+
  theme_bw()+
  theme(text=element_text(family= "Times New Roman"))+
  labs(title="QQPlot of Manova Model",
       subtitle = "Square Root Transformation",
       y= "Sample Quantiles",
       x= "Theoretical Quantities")

ggplot(data=temp8, aes(x=resid_vals))+
  geom_bar(stat="bin", bins=20, color= "black", fill = "white")+
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="Normality of Manova Model",
       subtitle = "Square Root Transformation",
       y= "Count",
       x= "Standardized Residuals")
```




