---
title: "running-MANOVA"
output:
  word_document: default
  html_document: default
date: "2022-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse)
library(readxl)
library(flextable)
library(extrafont)
library(writexl)
library(car) #Manova function
library(broom) #tidy function
library(emmeans) #emmeans function
```

```{r}
#times new roman tables
my_ft_theme <- function(ft, ...) {
  # Remove vertical cell padding
  ft <- padding(ft, padding.top = 0, padding.bottom = 0, part = "all")
  
  # Change font to TNR 11
  ft <- font(ft, fontname = "Times New Roman", part = "all")
  ft <- fontsize(ft, part = "all", size = 12)
  ft
}
```

```{r}

chosen_nona1 <- read_excel("C:\\Users\\kayna\\Documents\\headscan_dissertation\\chosen_nona1.xlsx")

chosen_nona1$gender <- as.factor(chosen_nona1$gender)
chosen_nona1$race_eth <- as.factor(chosen_nona1$race_eth)
chosen_nona1$age_group <- as.factor(chosen_nona1$age_group)

chosen_nona1$race_eth <- 
  recode_factor(chosen_nona1$race_eth, 'white'= "White")

summary(chosen_nona1)

chosen_nona1$gender <-
  recode_factor(chosen_nona1$gender, 'Female'= "Female/Other",
                'Other' = "Female/Other")

summary(chosen_nona1$gender)

variables <- cbind(chosen_nona1$AA_C, chosen_nona1$BiW_C, chosen_nona1$BiW_L, 
                   chosen_nona1$GoSub_C, chosen_nona1$NRB_L, chosen_nona1$ProS_L,
                   chosen_nona1$SelP_L, chosen_nona1$SelM_L, chosen_nona1$SnasM_C,
                   chosen_nona1$TrSman_C, chosen_nona1$TrTr_C, chosen_nona1$TrTr_L)
```

#https://www.hindawi.com/journals/cmmm/2019/2173638/ 
Use Pillai! better for when we don't know enough about covariance

#https://www.sagepub.com/sites/default/files/upm-assets/9761_book_item_9761.pdf
Type III sum of squares can be used in models where there are uneven group sizes, although there needs to be at least one participant in each cell. It calculates the sum of squares after the independent variables have all been adjusted for the inclusion of all other independent variables in the model


```{r}
output<-lm(variables ~ gender+race_eth+age_group, data=chosen_nona1,
           contrasts = list(gender=contr.sum, race_eth=contr.sum, age_group=contr.sum))

manova_out_nona1 <- Manova(output, type="III")

summary(manova_out_nona1)
```
#https://www.sagepub.com/sites/default/files/upm-assets/9761_book_item_9761.pdf
Type I, hierarchical or sequential sums of squares, is appropriate when the groups in the MANOVA are of equal sizes. Type I sum of squares provides a breakdown of the sums of squares for the whole model used in the MANOVA but it is particularly sensitive to the order in which the independent variables are placed in the model. If a variable is entered first, it is not adjusted for any of the other variables; if it is entered second, it is adjusted for one other variable (the first one entered); if it is placed third, it will be adjusted for the two other variables already entered. 

```{r}
output1<-manova(variables ~ gender+race_eth+age_group, data=chosen_nona1)

#type 3 and type 1 give same Pillai values

summary(output1)

```


```{r}
output2<-as.data.frame(tidy(output1))
output2$signif <- with(output2, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
output2$p.value <- formatC(output2$p.value, format = "e")

output2 <- rename(output2, f.statistic = statistic)

#Autofit Width Table TNR
flextable(output2) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Additive MANOVA Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```

From 511 notes: 

The experimentwise error rate (EER) is the probability of having at
least one false rejection in the group of tests from a single experiment
or study. The “experiment” is the ANOVA analysis.


John Tukey proposed a method that can be used to run all pairwise
comparisons while controlling EER.

Tukey ME > Unadj ME, hence we will find evidence of fewer
differences (or weaker evidence of differences) using Tukey’s
method.





```{r}
AA_Cout <- aov(AA_C ~ gender+race_eth+age_group, data=chosen_nona1)
summary(AA_Cout)
AA_Cout_data <- as.data.frame(tidy(AA_Cout))
```

```{r}
AA_Cout_data <- rename(AA_Cout_data, f.statistic = statistic)
AA_Cout_data$signif <- with(AA_Cout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
AA_Cout_data$p.value <- formatC(AA_Cout_data$p.value, format = "e")



AA_Cout_data <- AA_Cout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(AA_Cout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("AA_C Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
AA_Cg_em <- emmeans(AA_Cout, ~ gender)
AA_Cg_em1 <- as.data.frame(AA_Cg_em)

AA_Cg_em 

AA_Cg_em1<- AA_Cg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(AA_Cg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: AA_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


AA_Cg_em2 <- pairs(AA_Cg_em, adjust="Tukey")
AA_Cg_em3 <- as.data.frame(AA_Cg_em2)

AA_Cg_em3$signif <- with(AA_Cg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
AA_Cg_em3$p.value <- formatC(AA_Cg_em3$p.value, format = "e")

AA_Cg_em2

AA_Cg_em3<- AA_Cg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(AA_Cg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: AA_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_AA_Cg <- emmip(AA_Cout, ~ gender, CIs = TRUE)

emmip_AA_Cg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="AA_C and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
AA_Cr_em <- emmeans(AA_Cout, ~ race_eth)
AA_Cr_em1 <- as.data.frame(AA_Cr_em)

AA_Cr_em 

AA_Cr_em1<- AA_Cr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(AA_Cr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: AA_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


AA_Cr_em2 <- pairs(AA_Cr_em, adjust="Tukey")
AA_Cr_em3 <- as.data.frame(AA_Cr_em2)

AA_Cr_em3$signif <- with(AA_Cr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
AA_Cr_em3$p.value <- formatC(AA_Cr_em3$p.value, format = "e")



AA_Cr_em2


AA_Cr_em3<- AA_Cr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(AA_Cr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: AA_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_AA_Cr <- emmip(AA_Cout, ~ race_eth, CIs = TRUE)

emmip_AA_Cr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="AA_C and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```
```{r}
AA_Ca_em <- emmeans(AA_Cout, ~ age_group)
AA_Ca_em1 <- as.data.frame(AA_Ca_em)

AA_Ca_em 


AA_Ca_em1<- AA_Ca_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(AA_Ca_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: AA_C and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


AA_Ca_em2 <- pairs(AA_Ca_em, adjust="Tukey")
AA_Ca_em3 <- as.data.frame(AA_Ca_em2)

AA_Ca_em3$signif <- with(AA_Ca_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
AA_Ca_em3$p.value <- formatC(AA_Ca_em3$p.value, format = "e")

AA_Ca_em2



AA_Ca_em3<- AA_Ca_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(AA_Ca_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: AA_C and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_AA_Ca <- emmip(AA_Cout, ~ age_group, CIs = TRUE)

emmip_AA_Ca + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="AA_C and Age Group: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Age Group")
```










```{r}
BiW_Lout <- aov(BiW_L ~ gender+race_eth+age_group, data=chosen_nona1)
summary(BiW_Lout)
BiW_Lout_data <- as.data.frame(tidy(BiW_Lout))
```

```{r}
BiW_Lout_data <- rename(BiW_Lout_data, f.statistic = statistic)
BiW_Lout_data$signif <- with(BiW_Lout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
BiW_Lout_data$p.value <- formatC(BiW_Lout_data$p.value, format = "e")

BiW_Lout_data <- BiW_Lout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(BiW_Lout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("BiW_L Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
BiW_Lg_em <- emmeans(BiW_Lout, ~ gender)
BiW_Lg_em1 <- as.data.frame(BiW_Lg_em)

BiW_Lg_em 

BiW_Lg_em1 <- BiW_Lg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(BiW_Lg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: BiW_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


BiW_Lg_em2 <- pairs(BiW_Lg_em, adjust="Tukey")
BiW_Lg_em3 <- as.data.frame(BiW_Lg_em2)

BiW_Lg_em3$signif <- with(BiW_Lg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
BiW_Lg_em3$p.value <- formatC(BiW_Lg_em3$p.value, format = "e")

BiW_Lg_em2

BiW_Lg_em3 <- BiW_Lg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))


flextable(BiW_Lg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: BiW_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_BiW_Lg <- emmip(BiW_Lout, ~ gender, CIs = TRUE)

emmip_BiW_Lg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="BiW_L and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
BiW_Lr_em <- emmeans(BiW_Lout, ~ race_eth)
BiW_Lr_em1 <- as.data.frame(BiW_Lr_em)

BiW_Lr_em 

BiW_Lr_em1 <- BiW_Lr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(BiW_Lr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: BiW_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


BiW_Lr_em2 <- pairs(BiW_Lr_em, adjust="Tukey")
BiW_Lr_em3 <- as.data.frame(BiW_Lr_em2)

BiW_Lr_em3$signif <- with(BiW_Lr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
BiW_Lr_em3$p.value <- formatC(BiW_Lr_em3$p.value, format = "e")

BiW_Lr_em2


BiW_Lr_em3 <- BiW_Lr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(BiW_Lr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: BiW_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_BiW_Lr <- emmip(BiW_Lout, ~ race_eth, CIs = TRUE)

emmip_BiW_Lr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="BiW_L and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```
```{r}
BiW_La_em <- emmeans(BiW_Lout, ~ age_group)
BiW_La_em1 <- as.data.frame(BiW_La_em)

BiW_La_em 


BiW_La_em1 <- BiW_La_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(BiW_La_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: BiW_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


BiW_La_em2 <- pairs(BiW_La_em, adjust="Tukey")
BiW_La_em3 <- as.data.frame(BiW_La_em2)

BiW_La_em3$signif <- with(BiW_La_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
BiW_La_em3$p.value <- formatC(BiW_La_em3$p.value, format = "e")

BiW_La_em2


BiW_La_em3 <- BiW_La_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(BiW_La_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: BiW_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_BiW_La <- emmip(BiW_Lout, ~ age_group, CIs = TRUE)

emmip_BiW_La + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="BiW_L and Age Group: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Age Group")
```




```{r}
BiW_Cout <- aov(BiW_C ~ gender+race_eth+age_group, data=chosen_nona1)
summary(BiW_Cout)
BiW_Cout_data <- as.data.frame(tidy(BiW_Cout))
```

```{r}
BiW_Cout_data <- rename(BiW_Cout_data, f.statistic = statistic)
BiW_Cout_data$signif <- with(BiW_Cout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
BiW_Cout_data$p.value <- formatC(BiW_Cout_data$p.value, format = "e")


BiW_Cout_data <- BiW_Cout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(BiW_Cout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("BiW_C Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
BiW_Cg_em <- emmeans(BiW_Cout, ~ gender)
BiW_Cg_em1 <- as.data.frame(BiW_Cg_em)

BiW_Cg_em 


BiW_Cg_em1 <- BiW_Cg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(BiW_Cg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: BiW_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


BiW_Cg_em2 <- pairs(BiW_Cg_em, adjust="Tukey")
BiW_Cg_em3 <- as.data.frame(BiW_Cg_em2)

BiW_Cg_em3$signif <- with(BiW_Cg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
BiW_Cg_em3$p.value <- formatC(BiW_Cg_em3$p.value, format = "e")

BiW_Cg_em2

BiW_Cg_em3 <- BiW_Cg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(BiW_Cg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: BiW_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_BiW_Cg <- emmip(BiW_Cout, ~ gender, CIs = TRUE)

emmip_BiW_Cg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="BiW_C and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
BiW_Cr_em <- emmeans(BiW_Cout, ~ race_eth)
BiW_Cr_em1 <- as.data.frame(BiW_Cr_em)

BiW_Cr_em 

BiW_Cr_em1 <- BiW_Cr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))


flextable(BiW_Cr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: BiW_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


BiW_Cr_em2 <- pairs(BiW_Cr_em, adjust="Tukey")
BiW_Cr_em3 <- as.data.frame(BiW_Cr_em2)

BiW_Cr_em3$signif <- with(BiW_Cr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
BiW_Cr_em3$p.value <- formatC(BiW_Cr_em3$p.value, format = "e")

BiW_Cr_em2


BiW_Cr_em3 <- BiW_Cr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(BiW_Cr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: BiW_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_BiW_Cr <- emmip(BiW_Cout, ~ race_eth, CIs = TRUE)

emmip_BiW_Cr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="BiW_C and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```




```{r}
GoSub_Cout <- aov(GoSub_C ~ gender+race_eth+age_group, data=chosen_nona1)
summary(GoSub_Cout)
GoSub_Cout_data <- as.data.frame(tidy(GoSub_Cout))
```

```{r}
GoSub_Cout_data <- rename(GoSub_Cout_data, f.statistic = statistic)
GoSub_Cout_data$signif <- with(GoSub_Cout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
GoSub_Cout_data$p.value <- formatC(GoSub_Cout_data$p.value, format = "e")


GoSub_Cout_data <- GoSub_Cout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))


#Autofit Width Table TNR
flextable(GoSub_Cout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("GoSub_C Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
GoSub_Cg_em <- emmeans(GoSub_Cout, ~ gender)
GoSub_Cg_em1 <- as.data.frame(GoSub_Cg_em)

GoSub_Cg_em 


GoSub_Cg_em1 <- GoSub_Cg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(GoSub_Cg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: GoSub_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


GoSub_Cg_em2 <- pairs(GoSub_Cg_em, adjust="Tukey")
GoSub_Cg_em3 <- as.data.frame(GoSub_Cg_em2)

GoSub_Cg_em3$signif <- with(GoSub_Cg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
GoSub_Cg_em3$p.value <- formatC(GoSub_Cg_em3$p.value, format = "e")

GoSub_Cg_em2


GoSub_Cg_em3 <- GoSub_Cg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(GoSub_Cg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: GoSub_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_GoSub_Cg <- emmip(GoSub_Cout, ~ gender, CIs = TRUE)

emmip_GoSub_Cg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="GoSub_C and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
GoSub_Cr_em <- emmeans(GoSub_Cout, ~ race_eth)
GoSub_Cr_em1 <- as.data.frame(GoSub_Cr_em)

GoSub_Cr_em 


GoSub_Cr_em1 <- GoSub_Cr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(GoSub_Cr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: GoSub_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


GoSub_Cr_em2 <- pairs(GoSub_Cr_em, adjust="Tukey")
GoSub_Cr_em3 <- as.data.frame(GoSub_Cr_em2)

GoSub_Cr_em3$signif <- with(GoSub_Cr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
GoSub_Cr_em3$p.value <- formatC(GoSub_Cr_em3$p.value, format = "e")

GoSub_Cr_em2


GoSub_Cr_em3 <- GoSub_Cr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))


flextable(GoSub_Cr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: GoSub_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_GoSub_Cr <- emmip(GoSub_Cout, ~ race_eth, CIs = TRUE)

emmip_GoSub_Cr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="GoSub_C and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```
```{r}
GoSub_Ca_em <- emmeans(GoSub_Cout, ~ age_group)
GoSub_Ca_em1 <- as.data.frame(GoSub_Ca_em)

GoSub_Ca_em 


GoSub_Ca_em1 <- GoSub_Ca_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(GoSub_Ca_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: GoSub_C and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


GoSub_Ca_em2 <- pairs(GoSub_Ca_em, adjust="Tukey")
GoSub_Ca_em3 <- as.data.frame(GoSub_Ca_em2)

GoSub_Ca_em3$signif <- with(GoSub_Ca_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
GoSub_Ca_em3$p.value <- formatC(GoSub_Ca_em3$p.value, format = "e")

GoSub_Ca_em2


GoSub_Ca_em3 <- GoSub_Ca_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(GoSub_Ca_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: GoSub_C and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_GoSub_Ca <- emmip(GoSub_Cout, ~ age_group, CIs = TRUE)

emmip_GoSub_Ca + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="GoSub_C and Age Group: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Age Group")
```




```{r}
NRB_Lout <- aov(NRB_L ~ gender+race_eth+age_group, data=chosen_nona1)
summary(NRB_Lout)
NRB_Lout_data <- as.data.frame(tidy(NRB_Lout))
```

```{r}
NRB_Lout_data <- rename(NRB_Lout_data, f.statistic = statistic)
NRB_Lout_data$signif <- with(NRB_Lout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
NRB_Lout_data$p.value <- formatC(NRB_Lout_data$p.value, format = "e")

NRB_Lout_data <- NRB_Lout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(NRB_Lout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("NRB_L Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
NRB_Lg_em <- emmeans(NRB_Lout, ~ gender)
NRB_Lg_em1 <- as.data.frame(NRB_Lg_em)

NRB_Lg_em 


NRB_Lg_em1 <- NRB_Lg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(NRB_Lg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: NRB_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


NRB_Lg_em2 <- pairs(NRB_Lg_em, adjust="Tukey")
NRB_Lg_em3 <- as.data.frame(NRB_Lg_em2)

NRB_Lg_em3$signif <- with(NRB_Lg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
NRB_Lg_em3$p.value <- formatC(NRB_Lg_em3$p.value, format = "e")

NRB_Lg_em2

NRB_Lg_em3 <- NRB_Lg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(NRB_Lg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: NRB_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_NRB_Lg <- emmip(NRB_Lout, ~ gender, CIs = TRUE)

emmip_NRB_Lg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="NRB_L and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
NRB_Lr_em <- emmeans(NRB_Lout, ~ race_eth)
NRB_Lr_em1 <- as.data.frame(NRB_Lr_em)

NRB_Lr_em 

NRB_Lr_em1 <- NRB_Lr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(NRB_Lr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: NRB_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


NRB_Lr_em2 <- pairs(NRB_Lr_em, adjust="Tukey")
NRB_Lr_em3 <- as.data.frame(NRB_Lr_em2)

NRB_Lr_em3$signif <- with(NRB_Lr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
NRB_Lr_em3$p.value <- formatC(NRB_Lr_em3$p.value, format = "e")

NRB_Lr_em2

NRB_Lr_em3 <- NRB_Lr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(NRB_Lr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: NRB_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_NRB_Lr <- emmip(NRB_Lout, ~ race_eth, CIs = TRUE)

emmip_NRB_Lr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="NRB_L and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```





```{r}
ProS_Lout <- aov(ProS_L ~ gender+race_eth+age_group, data=chosen_nona1)
summary(ProS_Lout)
ProS_Lout_data <- as.data.frame(tidy(ProS_Lout))
```

```{r}
ProS_Lout_data <- rename(ProS_Lout_data, f.statistic = statistic)
ProS_Lout_data$signif <- with(ProS_Lout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
ProS_Lout_data$p.value <- formatC(ProS_Lout_data$p.value, format = "e")


ProS_Lout_data <- ProS_Lout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(ProS_Lout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("ProS_L Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
ProS_Lg_em <- emmeans(ProS_Lout, ~ gender)
ProS_Lg_em1 <- as.data.frame(ProS_Lg_em)

ProS_Lg_em 


ProS_Lg_em1 <- ProS_Lg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(ProS_Lg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: ProS_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


ProS_Lg_em2 <- pairs(ProS_Lg_em, adjust="Tukey")
ProS_Lg_em3 <- as.data.frame(ProS_Lg_em2)

ProS_Lg_em3$signif <- with(ProS_Lg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
ProS_Lg_em3$p.value <- formatC(ProS_Lg_em3$p.value, format = "e")

ProS_Lg_em2


ProS_Lg_em3 <- ProS_Lg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(ProS_Lg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: ProS_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_ProS_Lg <- emmip(ProS_Lout, ~ gender, CIs = TRUE)

emmip_ProS_Lg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="ProS_L and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
ProS_Lr_em <- emmeans(ProS_Lout, ~ race_eth)
ProS_Lr_em1 <- as.data.frame(ProS_Lr_em)

ProS_Lr_em 



ProS_Lr_em1 <- ProS_Lr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(ProS_Lr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: ProS_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


ProS_Lr_em2 <- pairs(ProS_Lr_em, adjust="Tukey")
ProS_Lr_em3 <- as.data.frame(ProS_Lr_em2)

ProS_Lr_em3$signif <- with(ProS_Lr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
ProS_Lr_em3$p.value <- formatC(ProS_Lr_em3$p.value, format = "e")

ProS_Lr_em2


ProS_Lr_em3 <- ProS_Lr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(ProS_Lr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: ProS_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_ProS_Lr <- emmip(ProS_Lout, ~ race_eth, CIs = TRUE)

emmip_ProS_Lr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="ProS_L and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```
```{r}
ProS_La_em <- emmeans(ProS_Lout, ~ age_group)
ProS_La_em1 <- as.data.frame(ProS_La_em)

ProS_La_em 

ProS_La_em1 <- ProS_La_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(ProS_La_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: ProS_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


ProS_La_em2 <- pairs(ProS_La_em, adjust="Tukey")
ProS_La_em3 <- as.data.frame(ProS_La_em2)

ProS_La_em3$signif <- with(ProS_La_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
ProS_La_em3$p.value <- formatC(ProS_La_em3$p.value, format = "e")

ProS_La_em2


ProS_La_em3 <- ProS_La_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(ProS_La_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: ProS_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_ProS_La <- emmip(ProS_Lout, ~ age_group, CIs = TRUE)

emmip_ProS_La + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="ProS_L and Age Group: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Age Group")
```




```{r}
SelP_Lout <- aov(SelP_L ~ gender+race_eth+age_group, data=chosen_nona1)
summary(SelP_Lout)
SelP_Lout_data <- as.data.frame(tidy(SelP_Lout))
```

```{r}
SelP_Lout_data <- rename(SelP_Lout_data, f.statistic = statistic)
SelP_Lout_data$signif <- with(SelP_Lout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SelP_Lout_data$p.value <- formatC(SelP_Lout_data$p.value, format = "e")


SelP_Lout_data <- SelP_Lout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(SelP_Lout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("SelP_L Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
SelP_Lg_em <- emmeans(SelP_Lout, ~ gender)
SelP_Lg_em1 <- as.data.frame(SelP_Lg_em)

SelP_Lg_em 

SelP_Lg_em1 <- SelP_Lg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelP_Lg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: SelP_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


SelP_Lg_em2 <- pairs(SelP_Lg_em, adjust="Tukey")
SelP_Lg_em3 <- as.data.frame(SelP_Lg_em2)

SelP_Lg_em3$signif <- with(SelP_Lg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SelP_Lg_em3$p.value <- formatC(SelP_Lg_em3$p.value, format = "e")

SelP_Lg_em2


SelP_Lg_em3 <- SelP_Lg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelP_Lg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: SelP_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_SelP_Lg <- emmip(SelP_Lout, ~ gender, CIs = TRUE)

emmip_SelP_Lg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="SelP_L and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
SelP_Lr_em <- emmeans(SelP_Lout, ~ race_eth)
SelP_Lr_em1 <- as.data.frame(SelP_Lr_em)

SelP_Lr_em 


SelP_Lr_em1 <- SelP_Lr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))


flextable(SelP_Lr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: SelP_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


SelP_Lr_em2 <- pairs(SelP_Lr_em, adjust="Tukey")
SelP_Lr_em3 <- as.data.frame(SelP_Lr_em2)

SelP_Lr_em3$signif <- with(SelP_Lr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SelP_Lr_em3$p.value <- formatC(SelP_Lr_em3$p.value, format = "e")

SelP_Lr_em2



SelP_Lr_em3 <- SelP_Lr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))


flextable(SelP_Lr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: SelP_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_SelP_Lr <- emmip(SelP_Lout, ~ race_eth, CIs = TRUE)

emmip_SelP_Lr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="SelP_L and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```
```{r}
SelP_La_em <- emmeans(SelP_Lout, ~ age_group)
SelP_La_em1 <- as.data.frame(SelP_La_em)

SelP_La_em 


SelP_La_em1 <- SelP_La_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelP_La_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: SelP_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


SelP_La_em2 <- pairs(SelP_La_em, adjust="Tukey")
SelP_La_em3 <- as.data.frame(SelP_La_em2)

SelP_La_em3$signif <- with(SelP_La_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SelP_La_em3$p.value <- formatC(SelP_La_em3$p.value, format = "e")

SelP_La_em2

SelP_La_em3 <- SelP_La_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelP_La_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: SelP_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_SelP_La <- emmip(SelP_Lout, ~ age_group, CIs = TRUE)

emmip_SelP_La + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="SelP_L and Age Group: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Age Group")
```




```{r}
SelM_Lout <- aov(SelM_L ~ gender+race_eth+age_group, data=chosen_nona1)
summary(SelM_Lout)
SelM_Lout_data <- as.data.frame(tidy(SelM_Lout))
```

```{r}
SelM_Lout_data <- rename(SelM_Lout_data, f.statistic = statistic)
SelM_Lout_data$signif <- with(SelM_Lout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SelM_Lout_data$p.value <- formatC(SelM_Lout_data$p.value, format = "e")

SelM_Lout_data <- SelM_Lout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(SelM_Lout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("SelM_L Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
SelM_Lg_em <- emmeans(SelM_Lout, ~ gender)
SelM_Lg_em1 <- as.data.frame(SelM_Lg_em)

SelM_Lg_em 

SelM_Lg_em1 <- SelM_Lg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelM_Lg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: SelM_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


SelM_Lg_em2 <- pairs(SelM_Lg_em, adjust="Tukey")
SelM_Lg_em3 <- as.data.frame(SelM_Lg_em2)

SelM_Lg_em3$signif <- with(SelM_Lg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SelM_Lg_em3$p.value <- formatC(SelM_Lg_em3$p.value, format = "e")

SelM_Lg_em2


SelM_Lg_em3 <- SelM_Lg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelM_Lg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: SelM_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_SelM_Lg <- emmip(SelM_Lout, ~ gender, CIs = TRUE)

emmip_SelM_Lg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="SelM_L and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
SelM_Lr_em <- emmeans(SelM_Lout, ~ race_eth)
SelM_Lr_em1 <- as.data.frame(SelM_Lr_em)

SelM_Lr_em 

SelM_Lr_em1 <- SelM_Lr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelM_Lr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: SelM_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


SelM_Lr_em2 <- pairs(SelM_Lr_em, adjust="Tukey")
SelM_Lr_em3 <- as.data.frame(SelM_Lr_em2)

SelM_Lr_em3$signif <- with(SelM_Lr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SelM_Lr_em3$p.value <- formatC(SelM_Lr_em3$p.value, format = "e")

SelM_Lr_em2

SelM_Lr_em3 <- SelM_Lr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelM_Lr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: SelM_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_SelM_Lr <- emmip(SelM_Lout, ~ race_eth, CIs = TRUE)

emmip_SelM_Lr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="SelM_L and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```
```{r}
SelM_La_em <- emmeans(SelM_Lout, ~ age_group)
SelM_La_em1 <- as.data.frame(SelM_La_em)

SelM_La_em 

SelM_La_em1 <- SelM_La_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelM_La_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: SelM_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


SelM_La_em2 <- pairs(SelM_La_em, adjust="Tukey")
SelM_La_em3 <- as.data.frame(SelM_La_em2)

SelM_La_em3$signif <- with(SelM_La_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SelM_La_em3$p.value <- formatC(SelM_La_em3$p.value, format = "e")

SelM_La_em2

SelM_La_em3 <- SelM_La_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SelM_La_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: SelM_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_SelM_La <- emmip(SelM_Lout, ~ age_group, CIs = TRUE)

emmip_SelM_La + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="SelM_L and Age Group: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Age Group")
```




```{r}
SnasM_Cout <- aov(SnasM_C ~ gender+race_eth+age_group, data=chosen_nona1)
summary(SnasM_Cout)
SnasM_Cout_data <- as.data.frame(tidy(SnasM_Cout))
```

```{r}
SnasM_Cout_data <- rename(SnasM_Cout_data, f.statistic = statistic)
SnasM_Cout_data$signif <- with(SnasM_Cout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SnasM_Cout_data$p.value <- formatC(SnasM_Cout_data$p.value, format = "e")

SnasM_Cout_data <- SnasM_Cout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(SnasM_Cout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("SnasM_C Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
SnasM_Cg_em <- emmeans(SnasM_Cout, ~ gender)
SnasM_Cg_em1 <- as.data.frame(SnasM_Cg_em)

SnasM_Cg_em 

SnasM_Cg_em1 <- SnasM_Cg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SnasM_Cg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: SnasM_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


SnasM_Cg_em2 <- pairs(SnasM_Cg_em, adjust="Tukey")
SnasM_Cg_em3 <- as.data.frame(SnasM_Cg_em2)

SnasM_Cg_em3$signif <- with(SnasM_Cg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SnasM_Cg_em3$p.value <- formatC(SnasM_Cg_em3$p.value, format = "e")

SnasM_Cg_em2


SnasM_Cg_em3 <- SnasM_Cg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SnasM_Cg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: SnasM_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_SnasM_Cg <- emmip(SnasM_Cout, ~ gender, CIs = TRUE)

emmip_SnasM_Cg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="SnasM_C and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
SnasM_Cr_em <- emmeans(SnasM_Cout, ~ race_eth)
SnasM_Cr_em1 <- as.data.frame(SnasM_Cr_em)

SnasM_Cr_em 

SnasM_Cr_em1 <- SnasM_Cr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SnasM_Cr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: SnasM_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


SnasM_Cr_em2 <- pairs(SnasM_Cr_em, adjust="Tukey")
SnasM_Cr_em3 <- as.data.frame(SnasM_Cr_em2)

SnasM_Cr_em3$signif <- with(SnasM_Cr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
SnasM_Cr_em3$p.value <- formatC(SnasM_Cr_em3$p.value, format = "e")

SnasM_Cr_em2

SnasM_Cr_em3 <- SnasM_Cr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(SnasM_Cr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: SnasM_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_SnasM_Cr <- emmip(SnasM_Cout, ~ race_eth, CIs = TRUE)

emmip_SnasM_Cr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="SnasM_C and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```





```{r}
TrSman_Cout <- aov(TrSman_C ~ gender+race_eth+age_group, data=chosen_nona1)
summary(TrSman_Cout)
TrSman_Cout_data <- as.data.frame(tidy(TrSman_Cout))
```

```{r}
TrSman_Cout_data <- rename(TrSman_Cout_data, f.statistic = statistic)
TrSman_Cout_data$signif <- with(TrSman_Cout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrSman_Cout_data$p.value <- formatC(TrSman_Cout_data$p.value, format = "e")

TrSman_Cout_data <- TrSman_Cout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(TrSman_Cout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("TrSman_C Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
TrSman_Cg_em <- emmeans(TrSman_Cout, ~ gender)
TrSman_Cg_em1 <- as.data.frame(TrSman_Cg_em)

TrSman_Cg_em 


TrSman_Cg_em1 <- TrSman_Cg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrSman_Cg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: TrSman_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


TrSman_Cg_em2 <- pairs(TrSman_Cg_em, adjust="Tukey")
TrSman_Cg_em3 <- as.data.frame(TrSman_Cg_em2)

TrSman_Cg_em3$signif <- with(TrSman_Cg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrSman_Cg_em3$p.value <- formatC(TrSman_Cg_em3$p.value, format = "e")

TrSman_Cg_em2

TrSman_Cg_em3 <- TrSman_Cg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrSman_Cg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: TrSman_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_TrSman_Cg <- emmip(TrSman_Cout, ~ gender, CIs = TRUE)

emmip_TrSman_Cg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="TrSman_C and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
TrSman_Cr_em <- emmeans(TrSman_Cout, ~ race_eth)
TrSman_Cr_em1 <- as.data.frame(TrSman_Cr_em)

TrSman_Cr_em 

TrSman_Cr_em1 <- TrSman_Cr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrSman_Cr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: TrSman_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


TrSman_Cr_em2 <- pairs(TrSman_Cr_em, adjust="Tukey")
TrSman_Cr_em3 <- as.data.frame(TrSman_Cr_em2)

TrSman_Cr_em3$signif <- with(TrSman_Cr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrSman_Cr_em3$p.value <- formatC(TrSman_Cr_em3$p.value, format = "e")

TrSman_Cr_em2

TrSman_Cr_em3 <- TrSman_Cr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrSman_Cr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: TrSman_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_TrSman_Cr <- emmip(TrSman_Cout, ~ race_eth, CIs = TRUE)

emmip_TrSman_Cr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="TrSman_C and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```
```{r}
TrSman_Ca_em <- emmeans(TrSman_Cout, ~ age_group)
TrSman_Ca_em1 <- as.data.frame(TrSman_Ca_em)

TrSman_Ca_em 

TrSman_Ca_em1 <- TrSman_Ca_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrSman_Ca_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: TrSman_C and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


TrSman_Ca_em2 <- pairs(TrSman_Ca_em, adjust="Tukey")
TrSman_Ca_em3 <- as.data.frame(TrSman_Ca_em2)

TrSman_Ca_em3$signif <- with(TrSman_Ca_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrSman_Ca_em3$p.value <- formatC(TrSman_Ca_em3$p.value, format = "e")

TrSman_Ca_em2


TrSman_Ca_em3 <- TrSman_Ca_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrSman_Ca_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: TrSman_C and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_TrSman_Ca <- emmip(TrSman_Cout, ~ age_group, CIs = TRUE)

emmip_TrSman_Ca + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="TrSman_C and Age Group: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Age Group")
```




```{r}
TrTr_Cout <- aov(TrTr_C ~ gender+race_eth+age_group, data=chosen_nona1)
summary(TrTr_Cout)
TrTr_Cout_data <- as.data.frame(tidy(TrTr_Cout))
```

```{r}
TrTr_Cout_data <- rename(TrTr_Cout_data, f.statistic = statistic)
TrTr_Cout_data$signif <- with(TrTr_Cout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrTr_Cout_data$p.value <- formatC(TrTr_Cout_data$p.value, format = "e")



TrTr_Cout_data <- TrTr_Cout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(TrTr_Cout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("TrTr_C Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
TrTr_Cg_em <- emmeans(TrTr_Cout, ~ gender)
TrTr_Cg_em1 <- as.data.frame(TrTr_Cg_em)

TrTr_Cg_em 


TrTr_Cg_em1 <- TrTr_Cg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Cg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: TrTr_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


TrTr_Cg_em2 <- pairs(TrTr_Cg_em, adjust="Tukey")
TrTr_Cg_em3 <- as.data.frame(TrTr_Cg_em2)

TrTr_Cg_em3$signif <- with(TrTr_Cg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrTr_Cg_em3$p.value <- formatC(TrTr_Cg_em3$p.value, format = "e")

TrTr_Cg_em2

TrTr_Cg_em3 <- TrTr_Cg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Cg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: TrTr_C and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_TrTr_Cg <- emmip(TrTr_Cout, ~ gender, CIs = TRUE)

emmip_TrTr_Cg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="TrTr_C and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
TrTr_Cr_em <- emmeans(TrTr_Cout, ~ race_eth)
TrTr_Cr_em1 <- as.data.frame(TrTr_Cr_em)

TrTr_Cr_em 

TrTr_Cr_em1 <- TrTr_Cr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Cr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: TrTr_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


TrTr_Cr_em2 <- pairs(TrTr_Cr_em, adjust="Tukey")
TrTr_Cr_em3 <- as.data.frame(TrTr_Cr_em2)

TrTr_Cr_em3$signif <- with(TrTr_Cr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrTr_Cr_em3$p.value <- formatC(TrTr_Cr_em3$p.value, format = "e")

TrTr_Cr_em2

TrTr_Cr_em3 <- TrTr_Cr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Cr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: TrTr_C and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_TrTr_Cr <- emmip(TrTr_Cout, ~ race_eth, CIs = TRUE)

emmip_TrTr_Cr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="TrTr_C and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```
```{r}
TrTr_Ca_em <- emmeans(TrTr_Cout, ~ age_group)
TrTr_Ca_em1 <- as.data.frame(TrTr_Ca_em)

TrTr_Ca_em 

TrTr_Ca_em1 <- TrTr_Ca_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Ca_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: TrTr_C and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


TrTr_Ca_em2 <- pairs(TrTr_Ca_em, adjust="Tukey")
TrTr_Ca_em3 <- as.data.frame(TrTr_Ca_em2)

TrTr_Ca_em3$signif <- with(TrTr_Ca_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrTr_Ca_em3$p.value <- formatC(TrTr_Ca_em3$p.value, format = "e")

TrTr_Ca_em2

TrTr_Ca_em3 <- TrTr_Ca_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Ca_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: TrTr_C and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_TrTr_Ca <- emmip(TrTr_Cout, ~ age_group, CIs = TRUE)

emmip_TrTr_Ca + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="TrTr_C and Age Group: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Age Group")
```




```{r}
TrTr_Lout <- aov(TrTr_L ~ gender+race_eth+age_group, data=chosen_nona1)
summary(TrTr_Lout)
TrTr_Lout_data <- as.data.frame(tidy(TrTr_Lout))
```

```{r}
TrTr_Lout_data <- rename(TrTr_Lout_data, f.statistic = statistic)
TrTr_Lout_data$signif <- with(TrTr_Lout_data, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrTr_Lout_data$p.value <- formatC(TrTr_Lout_data$p.value, format = "e")

TrTr_Lout_data <- TrTr_Lout_data %>% 
  mutate(across(where(is.numeric), round, digits=3))

#Autofit Width Table TNR
flextable(TrTr_Lout_data) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("TrTr_L Additive Anova Model Findings") %>% 
  fit_to_width(7.5) %>% 
  autofit()
```


```{r}
TrTr_Lg_em <- emmeans(TrTr_Lout, ~ gender)
TrTr_Lg_em1 <- as.data.frame(TrTr_Lg_em)

TrTr_Lg_em 

TrTr_Lg_em1 <- TrTr_Lg_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Lg_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: TrTr_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


TrTr_Lg_em2 <- pairs(TrTr_Lg_em, adjust="Tukey")
TrTr_Lg_em3 <- as.data.frame(TrTr_Lg_em2)

TrTr_Lg_em3$signif <- with(TrTr_Lg_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrTr_Lg_em3$p.value <- formatC(TrTr_Lg_em3$p.value, format = "e")

TrTr_Lg_em2

TrTr_Lg_em3 <- TrTr_Lg_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Lg_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: TrTr_L and Gender") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_TrTr_Lg <- emmip(TrTr_Lout, ~ gender, CIs = TRUE)

emmip_TrTr_Lg + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="TrTr_L and Gender: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Gender")
  
```


```{r}
TrTr_Lr_em <- emmeans(TrTr_Lout, ~ race_eth)
TrTr_Lr_em1 <- as.data.frame(TrTr_Lr_em)

TrTr_Lr_em 

TrTr_Lr_em1 <- TrTr_Lr_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Lr_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: TrTr_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


TrTr_Lr_em2 <- pairs(TrTr_Lr_em, adjust="Tukey")
TrTr_Lr_em3 <- as.data.frame(TrTr_Lr_em2)

TrTr_Lr_em3$signif <- with(TrTr_Lr_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrTr_Lr_em3$p.value <- formatC(TrTr_Lr_em3$p.value, format = "e")

TrTr_Lr_em2

TrTr_Lr_em3 <- TrTr_Lr_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_Lr_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: TrTr_L and Race/Ethnicity") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_TrTr_Lr <- emmip(TrTr_Lout, ~ race_eth, CIs = TRUE)

emmip_TrTr_Lr + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="TrTr_L and Race/Ethnicity: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Race/Ethnicity")
```
```{r}
TrTr_La_em <- emmeans(TrTr_Lout, ~ age_group)
TrTr_La_em1 <- as.data.frame(TrTr_La_em)

TrTr_La_em 

TrTr_La_em1 <- TrTr_La_em1 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_La_em1) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Estimated Marginal Means: TrTr_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


TrTr_La_em2 <- pairs(TrTr_La_em, adjust="Tukey")
TrTr_La_em3 <- as.data.frame(TrTr_La_em2)

TrTr_La_em3$signif <- with(TrTr_La_em3, ifelse(p.value < 0.05, 'TRUE', 'FALSE'))
TrTr_La_em3$p.value <- formatC(TrTr_La_em3$p.value, format = "e")

TrTr_La_em2

TrTr_La_em3 <- TrTr_La_em3 %>% 
  mutate(across(where(is.numeric), round, digits=3))

flextable(TrTr_La_em3) %>%
  my_ft_theme()%>% 
  bold(part = "header") %>% 
  set_caption("Tukey Pairwise Comparisons: TrTr_L and Age Group") %>% 
  fit_to_width(7.5) %>% 
  autofit()


emmip_TrTr_La <- emmip(TrTr_Lout, ~ age_group, CIs = TRUE)

emmip_TrTr_La + 
  theme_bw()+theme(text=element_text(family= "Times New Roman"))+
  labs(title="TrTr_L and Age Group: Estimated Marginal Means Plot",
       subtitle="With Confidence Intervals",
       y="Linear Prediction (of measurement in mm)",
       x="Levels of Age Group")
```


```{r}
#gender 
AA_Cg_em1$measure  <- "AA_C"
BiW_Lg_em1$measure  <- "BiW_L"
BiW_Cg_em1$measure  <- "BiW_C"
GoSub_Cg_em1$measure  <- "GoSub_C"
NRB_Lg_em1$measure  <- "NRB_L"
ProS_Lg_em1$measure  <- "ProS_L"
SelP_Lg_em1$measure  <- "SelP_L"
SelM_Lg_em1$measure  <- "SelM_L"
SnasM_Cg_em1$measure  <- "SnasM_C"
TrSman_Cg_em1$measure  <- "TrSman_C"
TrTr_Cg_em1$measure  <- "TrTr_C"
TrTr_Lg_em1$measure  <- "TrTr_L"

gender_means_data <- rbind(AA_Cg_em1, BiW_Lg_em1, BiW_Cg_em1, GoSub_Cg_em1, NRB_Lg_em1,
                    ProS_Lg_em1, SelP_Lg_em1, SelM_Lg_em1, SnasM_Cg_em1, TrSman_Cg_em1,
                    TrTr_Cg_em1, TrTr_Lg_em1)

#write_xlsx(gender_means_data, "C:\\Users\\19177\\OneDrive - Colostate\\Desktop\\Dissertation\\headscan_dissertation\\gender_means_data.xlsx")
```

```{r}
#race_eth
AA_Cr_em1$measure  <- "AA_C"
BiW_Lr_em1$measure  <- "BiW_L"
BiW_Cr_em1$measure  <- "BiW_C"
GoSub_Cr_em1$measure  <- "GoSub_C"
NRB_Lr_em1$measure  <- "NRB_L"
ProS_Lr_em1$measure  <- "ProS_L"
SelP_Lr_em1$measure  <- "SelP_L"
SelM_Lr_em1$measure  <- "SelM_L"
SnasM_Cr_em1$measure  <- "SnasM_C"
TrSman_Cr_em1$measure  <- "TrSman_C"
TrTr_Cr_em1$measure  <- "TrTr_C"
TrTr_Lr_em1$measure  <- "TrTr_L"

race_means_data <- rbind(AA_Cr_em1, BiW_Lr_em1, BiW_Cr_em1, GoSub_Cr_em1, NRB_Lr_em1,
                    ProS_Lr_em1, SelP_Lr_em1, SelM_Lr_em1, SnasM_Cr_em1, TrSman_Cr_em1,
                    TrTr_Cr_em1, TrTr_Lr_em1)

#write_xlsx(race_means_data, "C:\\Users\\19177\\OneDrive - Colostate\\Desktop\\Dissertation\\headscan_dissertation\\race_means_data.xlsx")
```

```{r}
#age 
AA_Ca_em1$measure  <- "AA_C"
BiW_La_em1$measure  <- "BiW_L"
GoSub_Ca_em1$measure  <- "GoSub_C"
ProS_La_em1$measure  <- "ProS_L"
SelP_La_em1$measure  <- "SelP_L"
SelM_La_em1$measure  <- "SelM_L"
TrSman_Ca_em1$measure  <- "TrSman_C"
TrTr_Ca_em1$measure  <- "TrTr_C"
TrTr_La_em1$measure  <- "TrTr_L"

age_means_data <- rbind(AA_Ca_em1, BiW_La_em1, GoSub_Ca_em1,
                    ProS_La_em1, SelP_La_em1, SelM_La_em1, TrSman_Ca_em1,
                    TrTr_Ca_em1, TrTr_La_em1)

#write_xlsx(age_means_data, "C:\\Users\\19177\\OneDrive - Colostate\\Desktop\\Dissertation\\headscan_dissertation\\age_means_data.xlsx")
```



```{r}
#gender 
AA_Cg_em3$measure  <- "AA_C"
BiW_Lg_em3$measure  <- "BiW_L"
BiW_Cg_em3$measure  <- "BiW_C"
GoSub_Cg_em3$measure  <- "GoSub_C"
NRB_Lg_em3$measure  <- "NRB_L"
ProS_Lg_em3$measure  <- "ProS_L"
SelP_Lg_em3$measure  <- "SelP_L"
SelM_Lg_em3$measure  <- "SelM_L"
SnasM_Cg_em3$measure  <- "SnasM_C"
TrSman_Cg_em3$measure  <- "TrSman_C"
TrTr_Cg_em3$measure  <- "TrTr_C"
TrTr_Lg_em3$measure  <- "TrTr_L"

gender_est_data <- rbind(AA_Cg_em3, BiW_Lg_em3, BiW_Cg_em3, GoSub_Cg_em3, NRB_Lg_em3,
                    ProS_Lg_em3, SelP_Lg_em3, SelM_Lg_em3, SnasM_Cg_em3, TrSman_Cg_em3,
                    TrTr_Cg_em3, TrTr_Lg_em3)

#write_xlsx(gender_est_data, "C:\\Users\\19177\\OneDrive - Colostate\\Desktop\\Dissertation\\headscan_dissertation\\gender_est_data.xlsx")
```

```{r}
#race_eth
AA_Cr_em3$measure  <- "AA_C"
BiW_Lr_em3$measure  <- "BiW_L"
BiW_Cr_em3$measure  <- "BiW_C"
GoSub_Cr_em3$measure  <- "GoSub_C"
NRB_Lr_em3$measure  <- "NRB_L"
ProS_Lr_em3$measure  <- "ProS_L"
SelP_Lr_em3$measure  <- "SelP_L"
SelM_Lr_em3$measure  <- "SelM_L"
SnasM_Cr_em3$measure  <- "SnasM_C"
TrSman_Cr_em3$measure  <- "TrSman_C"
TrTr_Cr_em3$measure  <- "TrTr_C"
TrTr_Lr_em3$measure  <- "TrTr_L"

race_est_data <- rbind(AA_Cr_em3, BiW_Lr_em3, BiW_Cr_em3, GoSub_Cr_em3, NRB_Lr_em3,
                    ProS_Lr_em3, SelP_Lr_em3, SelM_Lr_em3, SnasM_Cr_em3, TrSman_Cr_em3,
                    TrTr_Cr_em3, TrTr_Lr_em3)

#write_xlsx(race_est_data, "C:\\Users\\19177\\OneDrive - Colostate\\Desktop\\Dissertation\\headscan_dissertation\\race_est_data.xlsx")
```

```{r}
#age 
AA_Ca_em3$measure  <- "AA_C"
BiW_La_em3$measure  <- "BiW_L"
GoSub_Ca_em3$measure  <- "GoSub_C"
ProS_La_em3$measure  <- "ProS_L"
SelP_La_em3$measure  <- "SelP_L"
SelM_La_em3$measure  <- "SelM_L"
TrSman_Ca_em3$measure  <- "TrSman_C"
TrTr_Ca_em3$measure  <- "TrTr_C"
TrTr_La_em3$measure  <- "TrTr_L"

age_est_data <- rbind(AA_Ca_em3, BiW_La_em3, GoSub_Ca_em3,
                    ProS_La_em3, SelP_La_em3, SelM_La_em3, 
                    TrSman_Ca_em3, TrTr_Ca_em3, TrTr_La_em3)

#write_xlsx(age_est_data, "C:\\Users\\19177\\OneDrive - Colostate\\Desktop\\Dissertation\\headscan_dissertation\\age_est_data.xlsx")
```





